How is experience transformed into memory?

### 2018-09-02 paper/main.tex
finished draft of results

\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video.  This information included: a brief narrative description of what was happening; whether the scene took place indoors vs. outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annoted features see \textit{Methods}).  We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.  We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.  Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.  We found that 28 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).  Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.  However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single video.  Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).

@@

The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); or that involved Sherlock and Watson interacting (Fig.~\topics).  Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).  The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).  Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).  These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).  Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).  Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.  We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).  To create a stable ``summary'' of the video, we computed the avereage topic vector within each event (Fig.~\ref{fig:model}C).

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (34 events detected).  \textbf{C.} Average topic vectors for each of the 34 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (27 events detected).  \textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector.}
\label{fig:model}
\end{figure}

@@

Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).  Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.  To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).  As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.  As for the video correlation matrix, we can use an HMM, along with the aformentioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).  We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).

@@

The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common topic model and segmenting the content into events using HMMs.  Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.  One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector.  This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.  Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A); ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.  In list-learning studies, this set of analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.  However, in naturalistic recall the analyses provide a wholely incomplete picture: it leaves out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).

The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.  However, it is difficult to gain deep insights into that content by directly examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).  To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a 2-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.  In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflects the distances between their associated topic vectors (Fig.~\ref{fig:trajectory}A, B).

@@

\textbf{JRM STOPPED HERE}

% characterize gist of movie and recalls
% x1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
% x2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
% x3. question: do recalls exhibit same structure?  apply topic model to recalls.  note that by projecting everything into a common topic space, the thematic content of each moment of movie/recall can be compared, even though the mix of words used to describe any given event or moment may not be consistent across people (or across annotations/recall)
% x4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
% x5. match up events (correlations)
% x6. now we can use classic memory analyses to examine structure of recall.  motivate and reference PFR, lag-CRP, and SPC.  but this does not tell us about structure in the *content* of what people remembered, or whether people's recalls are capturing the hierarchical temporal structure of the original movie.
% 7. topic trajectories as a new way of characterizing recall.  assess agreement using rayleigh test.  also examine shapes of each subject's trajectory to show match.  key insight: everyone captures the general shape, but at different "sampling resolutions"
% 8. we can also project back onto the original (word) features to understand more about what any particular part of the trajectory reflects (wordle fig)
% 9. the above analyses tell us about how the trajectory of thematic content in the episode is both preserved and transformed in participants' memories.  we next carried out analyses to understand the neural bases of these phenomena.  analysis 1: which structures are sensitive (during viewing) to the original episode's topic trajectory?  answer: default mode.  anlaysis 2: which structure are sensitive (during viewing) to how the participants will later recall the episode?  answer: vmPFC, default mode.  (potential role of vmPFC in reflecting participant-specific memory transformations and processing)

To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}A).  We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure. To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events. We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius= 0.5) around the point and grouped together all recall transitions that intersected the circle (across participants). To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together. To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p < 0.001$, corrected at $p < 0.05$ using the permutation procedure described in Methods). Notably, the video events fell within the path formed by the recall events.  Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}B), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.

%NOTE: it feels like we need some more supporting evidence that the shape of the video and the recall trajectories are related.  one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per participant. the result is that hand annotated memory correlates to this distance, suggesting that participants who better capture the shape also have better memory on average.

\subsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/brains_panels}
\caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} \textbf{A.} The correlation matrix representing the temporal structure of the video model. Below it is a surface plot of brain regions whose activity patterns mirrored the correlational structure of video model during viewing.  \textbf{B.} The left matrix is S13's video-recall correlation matrix before warping. The yellow stars represent the path recovered by dynamic time warping. The right matrix is the result after warping. The same warping path was applied to the fMRI timeseries (separately for each participant). A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix. Significance threshold (p$<$.05) for both video and recall analyses derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
\label{fig:brainz}
\end{figure}

Previous work suggests that the brain may represent our experiences as ``events'' with different time scales in a nested hierarchy ~\citep{LernEtal11, ChenEtal17, BaldEtal17}. In this next analysis we asked: what brain regions mirror the event-like correlational structure of our topic-based video model during viewing? We used a searchlight procedure (see Methods for details) to identify regions whose timepoint-by-timepoint correlational structure matched the correlational structure of our model. This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.

While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events. For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~\corrmats). We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing. In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls. Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model. The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.~\ref{fig:brainz}).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/topics}
\caption{\small \textbf{Analysis of topics by event memorability.} \textbf{A.} Group-averaged correlation between each video event and closest recall event. Error bars represent 95\% confidence intervals. Stars indicate top (green) and bottom (red) 3 remembered events across participants \textbf{B.} Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g., the correlation values in A). The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events. The word sizes are proportional to the word's ``activation''. \textbf{C.} Trajectory represents the video event model embedded in a 2D space using UMAP. The large colored dots are video events. The small colored dots are individual recall events across all participants, where the colors correspond to the closest video event. The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.  The left side of the wordle circles contain words associated with the video event vector and the right side contains words associated with the average recall event vector.}
\label{fig:topics}
\end{figure}

\subsection*{Memorability by event and topics}
A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).  This allows for analysis (and visualization) of the language used when participants recounted their experiences.  In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the ``top'' words for the most and least memorable scenes.

To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participants (Fig.~\ref{fig:topics}A). We used event memorability to create a weighted average over all video event vectors, where video events with better memory were weighted more heavily. Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video. The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, as were scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}B). To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.  Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}B).

Then, we took a closer look at the themes contained in the top/bottom 3 events, using the memorability weights to select the top/bottom events. We performed the same analysis as described above, but separately for the video and average recall event vectors representing each of the top/bottom 3 remembered events. In Figure~\ref{fig:topics}C, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events. The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event. We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle. Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}B) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}C). These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.

\subsection*{Additional measures of naturalistic recall}
Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible. We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order''). All three of these metrics were correlated to hand-annotated memory performance across participants ($p < 0.05$, see Supplemental Materials Section 1 for details).

Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way. We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering, and semantic clustering \citep{HowaKaha02, PolyEtal09}. Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).

@@

\subsubsection*{Extracting events using a hidden Markov model}
The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats). To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM). Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}. To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17, Brainiak}.

>>>>

\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video used in their experiment.  This information included: a brief narrative description of what was happening; whether the scene took place indoors vs. outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).  We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.  We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.  Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.  We found that 28 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).  Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.  However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single video.  Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).

@@

The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily John-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).  Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).  The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).  Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).  These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).  Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).  Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.  We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).  To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (34 events detected).  \textbf{C.} Average topic vectors for each of the 34 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (27 events detected).  \textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector.}
\label{fig:model}
\end{figure}

@@

Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).  Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.  To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).  As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.  As for the video correlation matrix, we can use an HMM, along with the aforementioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).  We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).

@@

The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common (shared) topic model and segmenting the content into events using HMMs.  Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.  One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).  This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.  Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A; ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.  In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.  However, in naturalistic recall the analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).

The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.  However, it is difficult to gain deep insights into that content by directly examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).  To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.  In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).

@@

Visual inspection of the video and recall topic trajectories reveals a striking pattern.  First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).  To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?  For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).  We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).  Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B).  We observed that the locations traversed by nearly the entire the video trajectory exhibited such peaks.  In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).  This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.

Because our analysis framework projects the dynamic video content and participants' recalls onto a common topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).  For each video event, we can ask: for all participants who recalled that event, what was the average correlation (across participants) between the video event's topic vector and the recall event topic vectors from each participant?  This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).  (We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supplemental Materials}).  Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.  We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.  To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).  Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location; the address of the flat that Sherlock and John share) were best remembered.  An analogous analysis revealed which themes were poorly remembered; here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).  This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.  This suggests that what is retained in memory are the major plot elements (i.e., the overall ``gist'' of what happened), whereas the more minor details are prone to pruning.

In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.  Specifically, for any given event we can construct a wordle from that event's topic vector, and we can construct a similar wordle from the average topic vectors produced by all participants who recalled that event.  We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.  Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).  \textbf{[JRM NOTE: NEED SOME SORT OF ``POINT'' OR TAKE-AWAY FROM THIS ANALYSIS]}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/topics}
\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.  Error bars denote bootstrap-derived across-participant 95\% confidence intervals.  The stars denote the three best-remembered events (green) and worst-remembered events (red).  \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.  Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).  Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.  \textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.  The large dots denote video events and the smaller dots denote recalled events (same color scheme as Fig.~\ref{fig:trajectory}A).  Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).  Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
\label{fig:topics}
\end{figure}

The results thus far tell us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.  We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.  In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.  Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).  As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.  In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.  Specifically, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\corrmats).  As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe, suggesting that these regions may play a role in transforming each individual's experience into memory.

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/brains_panels}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.  These regions are sensitive to the narrative structure of the video.  \textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.  These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.  Both panels: the maps are thresholded at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

@@

\subsubsection*{Extracting events using a hidden Markov model}
The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats). To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM). Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}. To implement this analysis, we used the BrainIAK toolbox \citep{BaldEtal17, Brainiak}.
